An agent-based model for city networks based on interactions between firms

### 2019-09-30 slides.tex
Update on Overleaf.
.

\begin{enumerate}
    \item Generate $N=700$ cities with size following a power law $E_i \= E_0 \cdot i^{-\alpha}$ with $E_0 \= 10^{11}$ and $\alpha=1.1$ (computed on Europe for GDP with cities larger than 50.000 inhabitants)
    \item Distribute them randomly in space (\cite{simini2019testing} vs \cite{banos2011christaller})
    \item Create countries with k-means clustering ($C \eq 30$)
    \item Distribute sectors such that (i) smaller cities are more specialized and (ii) larger cities are more knowledge-based, with a one dimensional axis to position sectors $1/K \ldots 1$ where the density $f\left(k\right)$ follows a log-normal with $\left(\mu,\sigma\right)$ such that $\sqrt{\Var f} = K/2$ for the largest, $\sqrt{\Var f} = 1/K$ for the smallest
\end{enumerate}

@@

\texttt{}% dataverse

>>>>

\begin{enumerate}
    \item Generate $N \textrm{ = } 700$ cities with size following a power law $E_i \textrm{ = } E_0 \cdot i^{-\alpha}$ with $E_0 \textrm{ = } 10^{11}$ and $\alpha=1.1$ (computed on Europe for GDP with cities larger than 50.000 inhabitants)
    \item Distribute them randomly in space (\cite{simini2019testing} vs \cite{banos2011christaller})
    \item Create countries with k-means clustering ($C \eq 30$)
    \item Distribute sectors such that (i) smaller cities are more specialized and (ii) larger cities are more knowledge-based, with a one dimensional axis to position sectors $1/K \ldots 1$ where the density $f\left(k\right)$ follows a log-normal with $\left(\mu,\sigma\right)$ such that $\sqrt{\Var f} = K/2$ for the largest, $\sqrt{\Var f} = 1/K$ for the smallest
\end{enumerate}

@@

\texttt{https://doi.org/10.7910/DVN/UPX23S}
